Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced. According to PVsyst, we have to each case study:

\begin{itemize}
 	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct. Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution. Only HOMER Pro was left for comparison. However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
	\item Case study 3: only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $87$\%. Concerning our optimal solution, it was not found an error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary;
	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. We deployed this case study in the field; PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution, it was not found an error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries. We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $85.65$\%. Concerning our optimal solution, it was not found an error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries. We did not deploy this case study in the field to perform comparisons; our approach did not produce a feasible solution with the equipment list available. Only HOMER Pro was left for comparisons. However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
\end{itemize}

>>>>

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced. %According to PVsyst, we have to each case study:
%
%\begin{itemize}
 For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct. Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary.
For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution. Only HOMER Pro was left for comparison. However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary.

For case study 3, only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
For case study 4, PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $87$\%. Concerning our optimal solution, it was not found an error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary.
For case study 5, PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. We deployed this case study in the field; PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution, it was not found an error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary.

For case study 6, PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries. We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $85.65$\%. Concerning our optimal solution, it was not found an error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary.
For case study 7, PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries. We did not deploy this case study in the field to perform comparisons; our approach did not produce a feasible solution with the equipment list available. Only HOMER Pro was left for comparisons. However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
%\end{itemize}
